---
title: "Section 02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 06 Installing ggplot2
To install ggplot2 use:

> install.packages("ggplot2")

The next thing to do is import it using:
 > library(ggplot2)

```{r ggplot2_try}
library(ggplot2)
```

# 07 Plotting a point with ggplot
```{r ggplot2_try_2}
x <- 4
y <- 9
dat <- data.frame(x, y)
dat
#
# 
ggplot()+geom_point(data = dat, aes(x=x, y=y), size=5, color="blue")
ggplot()+geom_point(data = dat, aes(x=x, y=y), size=10, color="red")
```

# 08 Controlling axis properties

## Excercise 1

```{r ggplot_ex}
x_ <- c(2,5,1)
y_ <- c(6,4,9)
data_ <- data.frame(x_, y_)
data_
ggplot()+geom_point(data = data_, aes(x=x_, y=y_), size=5, color="blue")
```
## Part 2
```{r ex_part2}
ggplot() + geom_point(data = data_, aes(x=x_, y=y_), size=10, color="red") +
	scale_x_continuous(limits = c(0,15), breaks = seq(0,15,3)) + 
	scale_y_continuous(limits = c(0,15), breaks = seq(0,15,3))
```
# 09 More with color and shape
To learn more about [color](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf)
To learn more about [shape](http://sape.inf.usi.ch/quick-reference/ggplot2/shape)

```{r color_shape}
ggplot() + geom_point(data = data_, aes(x=x_, y=y_), size=3, color="forestgreen", shape=25) +
	scale_x_continuous(limits = c(0,15), breaks = seq(0,15,3)) + 
	scale_y_continuous(limits = c(0,15), breaks = seq(0,15,3))
```

# 10 Graphing Lines with ggplot

blue line from (1, 3) to (8, 10)
red line from (-2, 13) to (7,-5)


```{r lines}
# Coordinates to form the line
red_line_x <- c(1, 8)
red_line_y <- c(3, 10)

blue_line_x <- c(-2, 7)
blue_line_y <- c(13, -5)
# Data frames
data_red_line <- data.frame(red_line_x, red_line_y)
data_blue_line <- data.frame(red_line_x, red_line_y)

ggplot() + geom_line(data=data_red_line, aes(x=red_line_x, y=red_line_y, color="red"))
ggplot() + geom_line(data=data_blue_line, aes(x=blue_line_x, y=blue_line_y, color="green"))
```

# 11 More with Lines
## Equations of a line
$$y = 3x + 1$$
$$y = -5x - 7$$
$$y = 0.5x - 0.73$$
```{r more_lines}
x <- c(0,10)
# First function
y = 3*x + 1
dat_func <- data.frame(x, y)
dat_func
# Second function
y <- -5 *x - 7
dat_func2 <- data.frame(x, y)
dat_func2
# Third Function
y <- 0.5 *x - 0.73
dat_func3 <- data.frame(x, y)
dat_func3
```